SAT Competition 2020\tnoteref{title}

### 2021-01-11 paper/main.tex
z3 schedule

The greedy set cover technique focuses only on solving the ``solvable'' instances,
disregarding the time it would take to execute the obtained schedule. We can
also look at schedules that would fit in a prescribed time budget. A natural choice
of the budget seems to be the original time limit of \SI{5000}{\second}.

@@

We complemented ...

\newpage

>>>>

The greedy set cover technique focuses only on solving instances,
disregarding the time it would take to execute the obtained schedule. We can
also look at schedules that would fit in a prescribed time budget. A natural choice
of the budget seems to be the original time limit of \SI{5000}{\second}.

@@

We complemented this ``uniform time split'' schedule by formulating the schedule construction
problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
For each solver (and its configuration) $S$ we introduced an integer variable $R^S$ denoting 
the number of seconds $S$ will run in the new schedule. We then constructed a formula with the hard
constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one 
soft constraint for every instance $I$ of the form
\[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
(Note that while $R^S$ are variables, i.e.~unknowns, the $T^S_I$ are known constants in the formula.)

\begin{table}
\caption{TODO}
\label{tab:MainZ3Schedule}
\begin{center}
\begin{tabular}{lccc}
solver & taking up (s) & solving & contributes \\
\hline
Kissat-sc2020-unsat & 2523 & 219 & 219 \\
Relaxed\_LCMDCBDL\_newTech & 2180 & 234 & \phantom{0}59 \\
Kissat-sc2020-sat & 103 & \phantom{0}72 & \phantom{00}2 \\
MapleLCMDistChronoBT-DL-f2trc & \phantom{0}76 & \phantom{0}15 & \phantom{00}0 \\
cadical-alluip & \phantom{0}58 & \phantom{0}26 & \phantom{00}2 \\
Maple-LCM-Dist-alluip-trail & \phantom{0}34 & \phantom{0}12 & \phantom{00}1 \\
Maple\_CM+dist+sattime2s+- & \phantom{0}18 & \phantom{0}18 & \phantom{00}1 \\
CaDiCaL-sc2020 & \phantom{00}8 & \phantom{0}10 & \phantom{00}2 \\
\hline 
Total & 5000 & \phantom{0}-- & 286 \\ 
\end{tabular}
\end{center}
\end{table}

Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).

Its not clear how unique this is. Just take the total 286 and compare to uniform split -- that's the interesting bit, perhaps.
